Universal and varyiable leadership dimensions across human societies

### 2020-06-24 leadership_across_cultures_contexts.Rmd
Change to Word for Re Re submisson.
Change to title.

---
title: "Universal and varying leadership dimensions across human societies"
author: "Zachary H. Garfield, Kristen L. Syme, and Edward H. Hagen"
date: "4/25/2019"
output: 
  bookdown::html_document2:
    number_sections: true
bibliography: Leader2.bib
csl: apa-6th-edition.csl
---

>>>>

---
title: "Universal and varyiable leadership dimensions across human societies"
author: "Zachary H. Garfield, Kristen L. Syme, and Edward H. Hagen"
date: "4/25/2019"
output: 
  bookdown::word_document2:
    number_sections: true
bibliography: Leader2.bib
csl: apa-6th-edition.csl
---
